FoRTE baseline

### 2019-10-11 analysis/paper/paper.Rmd
Move PFT plots to their own R script
Add pairs plot figure and text

Trajectories of species composition also varied widely by model configuration (Figure X, Y).
Under all configurations, most ensemble members were dominanted by a single PFT, and the sustained presence of more than 2 PFTs was limited to only a handful specific ensemble members across all configurations.
However, _which_ PFT was dominant varied depending on the parameter combination.

However, the ensemble spread around the mean was large:
across all configurations (except the finite canopy - two-stream radiative transfer cases), the spread in net primary productivity was from zero to nearly twice as high as the observation.
Ensemble variance in leaf area index was lower on average but, in some cases (especially the combination of finite canopy and multiple-scatter radiative transfer) was over an order of magnitude.
The predicted Shannon diversity index of plant functional types was, on average, higher in simulations when the canopy architecture was finite rather than closed.

```{r pairs-time, fig.cap = pairs_time_cap}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type.",
  "Each point indicates a single ensemble run with a different parameter combination.",
  "Letter labels are selected runs with the same parameters,",
  "and match the rows in Figure 4."
)
readd(pairs_time_averaged_knit)
```

<!-- TODO Use peak instead of post-1975? -->
<!-- TODO Use a logarithmic, rather than a linear fit? -->

Model configuration affected the emergent relationship between net primary productivity and leaf area index (Figure 3).
The crown model (closed vs. finite) had the strongest effect:
Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Although many simulations matched _either_ the observed net primary productivity or the observed leaf area index, only a few individual runs matched _both_.

>>>>

Trajectories of species composition also varied widely by model configuration (Figure X, Y).
Under all configurations, most ensemble members were dominanted by a single PFT, and the sustained presence of more than 2 PFTs was limited to only a handful specific ensemble members across all configurations.
However, _which_ PFT was dominant varied depending on the parameter combination, and any of the four PFTs became the dominant one some subset of simulations.

```{r pairs-time, fig.cap = pairs_time_cap}
pairs_time_cap <- paste(
  htmlfig(),
  "ED2 predictions of annual mean NPP and growing-season LAI in 1920, 1950, and 1999",
  "by model type.",
  "Each point indicates a single ensemble run with a different set of parameters.",
  "Solid line is the best-fit generalized additive model (GAM).",
  "Dashed lines indicate the error bounds of present-day observed NPP and LAI."
)
readd(npp_lai_pairs_knit)
```

<!-- TODO Use a logarithmic, rather than a linear fit? -->

The emergent relationship between NPP and LAI was similar across model configurations early in the runs, but became more sensitive to model configuration later into the runs.
Specifically, compared to runs with the default closed canopy, runs with a finite canopy were more likely to have higher LAI values for the same level of NPP, especially later into the simulation.
Although many simulations matched _either_ the observed net primary productivity or the observed leaf area index, only a small minority of individual runs matched _both_.
